---
title: "Syllabus"
output:
  html_document:
    includes:
      after_body: include/nothing.html
---

```{r include = FALSE}
library(dplyr)
library(stringr)
```

```{r include = FALSE}
# Import schedule
rawdat <- read.csv(file.path("course-admin", "schedule_2016.csv"), stringsAsFactors = FALSE)
rawdat$course <- as.factor(rawdat$course)

# Class meetings
rawdat_cm <- subset(rawdat, rawdat$course=="STAT540")  %>% droplevels()

cdat <- rawdat_cm %>%
  mutate(ugly_date = ISOdate(2014, match(month, tolower(month.name)), day),
         date = sprintf("%s-%02d %s",
                        tolower(months(ugly_date, abbreviate = TRUE)),
                        day, dow),
         notes = ifelse(grepl("^lect", lect) & raw_notes != "",
                        sprintf("%s: %s", lect, raw_notes), raw_notes))
cdat %>% head(3)

## link to the class page of any class meetings where such exists
cmdat <-
  data.frame(pdf = list.files(pattern = '^lect.*pdf$'),
             stringsAsFactors = FALSE)
cmdat <- cmdat %>% mutate(lect = str_extract(pdf, "lect[0-9]+"))
cdat <- cdat %>% left_join(cmdat)

cdat <- cdat %>%
  mutate(pdf_exists = Negate(is.na)(pdf))
cdat$notes[cdat$pdf_exists] <-
  str_replace(cdat$notes[cdat$pdf_exists],
              "(lect[0-9]{2})|(lect[1-9]{2})", '<a href="LINK">\\1</a>')
cdat <- cdat %>% mutate(notes = str_replace(notes, "LINK", pdf))
dat_cm <- cdat %>% split(cdat$course)
dat_cm <- lapply(dat_cm, 'rownames<-', NULL)

#Seminar meetings
rawdat_sm <- read.csv(file.path("course-admin", "seminar-meetings.csv"),
                   stringsAsFactors = FALSE,
                   colClasses = list(course = 'factor', dow = 'factor'))
sdat <- rawdat_sm %>%
  mutate(ugly_date = ISOdate(2014, match(month, tolower(month.name)), day),
         date = sprintf("%s-%02d %s",
                        tolower(months(ugly_date, abbreviate = TRUE)),
                        day, dow),
         notes = ifelse(grepl("^sm", sm) & raw_notes != "",
                        sprintf("%s: %s", sm, raw_notes), raw_notes))
sdat %>% head(3)

## link to the page of any seminar where such exists
smdat <-
  data.frame(html = list.files(pattern = '^sm.*html$'),
             stringsAsFactors = FALSE)
smdat <- smdat %>% mutate(sm = str_extract(html, "sm[0-9]+[a-c]"))

sdat <- sdat %>% left_join(smdat)

#seminar 00 from STAT545
sdat$html[sdat$sm=="sm00"] <-c('https://stat545-ubc.github.io/topics.html')

#separate links to seminar 01 parts
sdat$html[sdat$sm=="sm01a"] <-c('https://stat545-ubc.github.io/git01_git-install.html')

sdat$html[sdat$sm=="sm01c"] <-c('sm01c_biology-intro.pdf')

#separate links to seminar 02 parts
sdat$html[sdat$sm=="sm02a"] <-c('https://stat540-ubc.github.io/sm02a_rMarkdown.html')

sdat$html[sdat$sm=="sm02b"] <-c('https://stat540-ubc.github.io/sm02b_introProbCltLln.html')


sdat <- sdat %>%
  mutate(html_exists = Negate(is.na)(html))
sdat$notes[sdat$html_exists] <-
  str_replace(sdat$notes[sdat$html_exists],
              "(sm[0-9]{2})", '<a href="LINK">\\1</a>')
sdat <- sdat %>% mutate(notes = str_replace(notes, "LINK", html))

dat_sm <- sdat %>% split(sdat$course)
dat_sm <- lapply(dat_sm, 'rownames<-', NULL)
```

### Prerequisites.

Officially none BUT here in reality ...

**Statistics**: you should have already taken university level introductory statistics course.

**Biology**: no requirements, but you are expected to learn things like the difference between a DNA and RNA and a gene and a genome.

**R**: no experience required but be prepared to do a lot of self-guided learning. Go ahead and start now by installing R and the HIGHLY RECOMMENDED "integrated development environment" (IDE) RStudio! Students are expected to run R on their own computer or a computer they have plenty of access to and control over. The best set-up, if possible, is to bring your own laptop to the computing seminars.

### Evaluation

**Homework**: two assignments worth 20 points each. Homework #1 due Mon March 2. Homework #2 due Monday March 30. Instructions for how to submit your work are posted in the Assignment tab (see calendar below).

**Peer review**: you will be reviewing, commenting on, and marking other students’ assignments. This is a mandatory part of the course and you will be marked on your peer reviews (5 points for each HW, i.e., 10% of overall course mark). Additional guidelines will be given when homework is assigned. 

**Group project**: groups formed and projects conceived during January/February (see calendar below). Primary deliverable is a poster, presented in last class meeting (Wed April 8). Each student also produces a short report. 40 points. More information will be posted shortly.

**Participation**: 10 points for "other", including participation in class, seminars, and discussion forum, engagement with small computing exercises.


<!-- unholy hack to make following two tables less wide and the same wide -->
<style type="text/css">
table {
   max-width: 70%;
}
</style>

### Class mettings

**Time** : Mon Wed 9:30 - 11am

**Location** : ESB 4192

**Calendar**

```{r results = 'asis', echo = FALSE}
knitr::kable(dat_cm[["STAT540"]] %>% select(date, notes, instructor))
```

### Seminars

**Time**: Wed 12pm - 1pm (but welcome to come after class around 11am)

**Location**: ESB 1042 and 1046

**Calendar**

```{r results = 'asis', echo = FALSE}
knitr::kable(dat_sm[["STAT540-Seminar"]] %>% select(date, notes, TA))
```
